Example and Tutorial for Atom, Git, Github, etc Set-up for Linux

### 2019-12-29 nontex/install/linux/fn_ubuntu.Rmd
start vim set-up and knowledge file

```{bash}
# install atom
sudo apt-get install atom
```

@@

```{bash}
apt-get update
apt-get install r-base r-base-dev
```

>>>>

```{bash}
# install atom
sudo apt-get install atom
# install various atom packages that are necessary
apm install vim-mode-plus
```

@@

```{bash}
# Debian R is maintained by Johannes Ranke, copied from https://cran.r-project.org/bin/linux/debian/:
apt-key adv --keyserver keys.gnupg.net --recv-key 'E19F5F87128899B192B1A2C2AD5F960A256A04AF'
# Add to source.list, for debian stretch (9)
# sudo su added for security issue as super-user
sudo su -c "sudo echo 'deb http://cloud.r-project.org/bin/linux/debian stretch-cran35/' >> /etc/apt/sources.list"
# if added wrong lines, delete 3rd line
sudo sed '3d' /etc/apt/sources.list

# Update and Install R, should say updated from cloud.r
sudo apt-get update
sudo apt-get install r-base r-base-dev
```

# Install Other Programs and Packages

Other key programs and packages to install.

- vim: faster editor, on lower resource machines, atom is slow and typing could feel laggy.
- htop: for resource monitoring

```
sudo apt-get install vim
sudo apt-get install htop
```
